% add to Table of content
\addcontentsline{toc}{part}{ACKNOWLEDGMENTS}

% set 0 indentation
\setlength{\parindent}{0in}
% set paragraph space = 1 space
\setlength{\parskip}{1em}
% set line space = 1
\setlength{\baselineskip}{1.6em}

\begin{center}
  \fontsize{14}{17}\selectfont{\textbf{
      ACKNOWLEDGMENTS
    }} \\
\end{center}
\vspace{36pt}

This study would not have been completed without the support of many people. I would like to thank to Prof. Matthew N. Dailey, who is my main advisor. He interviewed and accepted me when I applied for the Master's degree in Data Science and Artificial Intelligence, which is leading me to the professional environment. On the academic level, he taught me the fundamentals of Machine Learning up to the latest advances in the field, and no other course on the internet could have been better. Under his supervision, I have developed skills such as coding, time management, working under pressure, and always challenging myself. On a personal level, he motivated me with his hard work, improving me from the previous version. To summarize, I am honestly grateful for support during my research time.

Secondly, I would like to thank Dr. Chaklam Silapasuwanchai who taught me the basics of Python and Machine Learning techniques, and also gave many a good recomendations. He gives great explainations of machine learning, invaluable advice, and insightful intuition.

Furthermore, I would like to appreciate all of the lecturers, secretaries, and staff in the Department of Information and Communication Technologies (ICT), and the Data Science and Artificial Intelligence degree program in the school of Engineering and Technology, AIT for their lessons, instructions, assistance, and support. In addition, I would like to thank all of my close friends at the Asian Institute of Technology and Kasetsart University for the good memories.

Last but not least, I would like to express my deepest gratitude to my parents, Mr. Thuanthong Boonchan and Mrs. Phatchari Boonchan, as well as my brother, Mr. Sittiphol Boonchan. This thesis might never have been completed without their attention and infinite support.